Metabolites reflect variability introduced by mesoscale eddies in the North Pacific Subtropical Gyre

### 2024-07-05 manuscript/manuscript.Rmd
Adding Importance statement

>>>>

# Importance

Mesoscale eddies are common ocean surface currents that circulate seawater vertically and horizontally. This stirring effect causes shifts in the ocean's biogeochemistry and community composition that presumably alter the functions and fluxes of the organisms in this surface environment, but this has not been measured directly. In this article, we used metabolomics to determine the effect eddies have on the quantity and composition of the organic carbon produced in the surface ocean. We found that many small, polar molecules track with overall biomass but that there were significant differences between the eddy states. We also found that a few metabolites stand out as biomarkers of eukaryotic phytoplankton enrichment under the higher nutrient supply from depth. This work answers outstanding questions about the importance of these common ocean features in marine flux models.
